Rate Transfers with Polyhedral Surrogate Losses /\\ Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-19 rates-neurips-21/rates.tex
labels for main theorems

%\begin{theorem}[Linear bounds for polyhedral surrogates]
\begin{theorem}[Main surrogate regret bound]
  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
\end{theorem}

We will also show a class of counterexamples for surrogate losses that are far from polyhedral, i.e. those that are smooth and strongly convex.
This could be viewed as a partial converse, providing evidence that some element of ``piecewise-linearity'' is \emph{necessary} for optimal surrogate regret bounds.
\begin{theorem}[Main lower bound]
  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}

>>>>

%\begin{theorem}[Linear bounds for polyhedral surrogates]
\begin{theorem}[Main surrogate regret bound]
  \label{thm:main-upper}
  Let $L$ be any polyhedral surrogate and $\psi$ any link function such that $(L,\psi)$ is consistent for the target loss $\ell$.
  Then $(L,\psi)$ guarantee a linear regret transfer rate for $\ell$.
  %Then there exists a surrogate regret bound with a linear transfer function $\zeta$.
\end{theorem}

We will also show a class of counterexamples for surrogate losses that are far from polyhedral, i.e. those that are smooth and strongly convex.
This could be viewed as a partial converse, providing evidence that some element of ``piecewise-linearity'' is \emph{necessary} for optimal surrogate regret bounds.
\begin{theorem}[Main lower bound]
  \label{thm:main-lower}
  Let $L$ be a differentiable convex surrogate, with locally Lipschitz gradient, which is locally strongly convex.
  If $L$ satisfies a regret transfer rate of $\zeta$ for a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
%  If $\zeta$ is a transfer function in a surrogate regret bound for $L$ to a target loss $\ell$, then there exists $c>0$ such that, for arbitrarily small $\epsilon>0$, we have $\zeta(\epsilon) \geq c\cdot\sqrt{\epsilon}$.
\end{theorem}
